Using Information Underlying Missing Data to Improve Estimation of NFL Field Goal Kicker Accuracy

### 2016-11-19 JaradNiemi_MwSAM2016.Rnw
Make urls smaller

<<informative_missing_plot, dependson="informative_missing_data">>=
ggplot(p_d, aes(dist, probability, color=Surface)) +
#  geom_point(data=fg_dist2, aes(dist, p, size=n)) +
  geom_line(aes(group=Surface)) +
  facet_grid(kicker_hidden ~.) +
  theme_bw() +
  labs(x="Distance (yards)",y="Probability of making the kick", size="Number of\nattempts") +
  ylim(0,1) +
  scale_color_manual(values = c("Grass" = "seagreen", "Synthetic" = "Black"))
@
\end{frame}

@@

These slides are available at 
\begin{itemize}
\item \url{}
\item or on my website \url{}.
\end{itemize}

>>>>

<<informative_missing_plot, dependson="informative_missing_data", fig.width=10, out.width="\\textwidth">>=
ggplot(p_d, aes(dist, probability, color=Surface)) +
#  geom_point(data=fg_dist2, aes(dist, p, size=n)) +
  geom_line(aes(group=Surface)) +
  facet_grid(kicker_hidden ~.) +
  theme_bw() +
  labs(x="Distance (yards)",y="Probability of making the kick", size="Number of\nattempts") +
  ylim(0,1) +
  scale_color_manual(values = c("Grass" = "seagreen", "Synthetic" = "Black"))
@
\end{frame}

@@

These slides are available at 
\begin{itemize}
\item {\scriptsize \url{https://github.com/jarad/MwSAM2016/raw/master/JaradNiemi_MwSAM2016.pdf}}
\item or on my website {\scriptsize \url{http://www.jarad.me/research/presentations.html}}.
\end{itemize}
